paper1_results_figs_slimmed_50_rr

### 2017-01-03 inst/documents/paper1/paper1_results_figs_slimmed_50_rr.Rmd
increase font size in fig 8

    #adds in no. scenarios correctly and incorrectly classified
    #cex to set textsize (0.7 all text doesn't quite fit in), good that A&B are now same size
    #round=0 to make boxes square
    #split.font=1 to stop bold text in labels
    prp(tree, extra=1, varlen = 0, main=main, box.col=cols, under=TRUE, 
        cex=0.4, round=0, split.font=1, ycompress = TRUE )
  }

>>>>

    #adds in no. scenarios correctly and incorrectly classified
    #cex to set textsize, good that A&B are now same size
    #round=0 to make boxes square
    #split.font=1 to stop bold text in labels
    prp(tree, extra=1, varlen = 0, main=main, box.col=cols, under=TRUE, 
        cex=0.6, round=0, split.font=1, ycompress = TRUE,
        eq="\n= ", lt="\n< ", ge="\n>= " )
  }
